Real-time resolving assembly graph by ONT long reads data

### 2019-11-01 paper.tex
sf

\title{Online resolving assembly graph by ONT long reads data}
\shorttitle{Real-time Scaffolding with Assembly graph}

@@

%Set abstract (see below)
\abstract{
A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either better control of sequencing resources or quick turnaround of analyses. The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies. Here we present another real-time hybrid assembler, \npgraph{}, that work on the assembly graph instead of the pre-assembled contigs. The results show improved accuracy while still minimize the required computational cost. The tool is available at \url{https://github.com/hsnguyen/assembly}.
}

@@

\subsection*{Scaffolding metagenomics data set}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Conclusions}
Assembly graph is the data structure describing the assembly process at a lower level of more details.
The current chapter brings this informative knowledge to the original \npscarf{}'s mechanism in two ways, either partly for the gap-filling module only (\npscarfg{}) or completely as the building block of the assembly construction method (\npgraph{}).

While the first approach showed improvements in terms of base's accuracy for the final results, it had limited ability in rectifying the mis-assemblies from the original version due to false positive alignments at contig level.
The issue can be tackled by applying the assembly graph completely as in \npgraph{}.
With a more conservative bridging method applied, the new method may consume more data to confidently construct the assembly but at the same time, the number of mis-located fragments has reduced significantly.
Furthermore, users can monitor the assembly in an interactive way providing the assembly GUI.

Compared to the other hybrid assemblers of similar methodology, such as $\mathtt{hybridSPAdes}$ and \unicycler{}, there are still rooms for further development of \npgraph{}. 
More comprehensive pre-processing step is needed for a better input graph possible since it would affect the completeness of final results. 
Importantly, a robust real-time voting system should be implemented to be able to detect the most probable path amongst all candidates in an efficient way.
This would alleviate the data consumption of the \npgraph{} while at the same time, maintain high confident and accurate scaffolding.

@@

It is worth noting that due to dead-ends, there not always exist a path in the assembly graph connecting two anchors as suggested by the alignments. In this case, if enough long reads coverage (20X) are met, a consensus module is invoked and the resulting sequence is contained in a \emph{pseudo} edge.
\subsection{Resolve the graph by reducing its complexity}

Whenever a bridge is finished (with only one path left), the assembly graph is \emph{transformed} or \emph{reduced} by replacing its unique path by an composite edge and removing any unique edges (edges coming from unique nodes) along the path. The assembly graph would have at least one edge less than the original after the reduction. The nodes located on the reduced path, other than 2 ends, also have their multiplicities subtracted by one and the bridge is marked as finally resolved without any further modifications.

>>>>

\title{Real-time resolving assembly graph by ONT long reads data}
\shorttitle{Real-time Scaffolding with Assembly graph}

@@

%Set abstract (see below)
\abstract{
A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either saving sequencing resources or reducing turnaround time for data analyses. The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies compared to other graph-based methods. 
Here we present \npgraph{}, a real-time hybrid assembly software using the assembly graph instead of the separated pre-assembly contigs. It is able to produce more complete genome assembly by resolving the path finding problem on the assembly graph using long reads as the traversing guide. 
The applications on synthetic and real data set of isolate genomes show improved accuracy while still maintain the required computational cost at very low level. In addition, the GUI feature can provide users a comprehensive look-and-feel of the whole assembly process. The tool and source code is available at \url{https://github.com/hsnguyen/assembly}.
}

@@

\subsection*{Metagenomics assembly}
We further used \npgraph{} on three mock communities to study the performance of this approach in metagenomics co-assembly application.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Conclusions}
Assembly graph is the data structure describing the assembly components at  more details.
The current chapter brings this informative knowledge to the original \npscarf{}'s mechanism in two ways, either partly for the gap-filling module only (\npscarfg{}) or completely as the building block for the assembly construction method (\npgraph{}).

While the first approach showed improvements in terms of base's accuracy for the final results, it had limited ability in rectifying the mis-assemblies from the original version due to false positive alignments at contig level.
The issue can be tackled by applying the assembly graph completely as in \npgraph{}.
With a more conservative bridging method applied, the new method may consume more data to confidently construct the assembly but at the same time, the number of mis-located fragments has reduced significantly.
Furthermore, users can monitor the assembly in an interactive manner providing the assembly GUI.

Compared to the other hybrid assemblers of similar methodology, such as $\mathtt{hybridSPAdes}$ and \unicycler{}, there are still rooms for further development of \npgraph{}. 
More comprehensive pre-processing step is needed for a better input graph possible since it would affect the completeness of final results.

Importantly, a robust real-time voting system should be implemented to be able to detect the most probable path amongst all candidates in an efficient way.
This would alleviate the data consumption of the \npgraph{} while at the same time, maintain high confident and accurate scaffolding.

@@

It is worth noting that due to dead-ends, there not always exist a path in the assembly graph connecting two anchors as suggested by the alignments. In this case, if enough long reads coverage (20X) are met, a consensus module is invoked and the resulting sequence is contained in a \emph{pseudo} edge.
\subsection*{Assembly graph resolving in real-time}
\npgraph{} resolves the graph by reducing its complexity perpetually using the long reads that could be generated in real-time.
Whenever a bridge is finished (with only one path left), the assembly graph is \emph{transformed} or \emph{reduced} by replacing its unique path by an composite edge and removing any unique edges (edges coming from unique nodes) along the path. The assembly graph would have at least one edge less than the original after the reduction. The nodes located on the reduced path, other than 2 ends, also have their multiplicities subtracted by one and the bridge is marked as finally resolved without any further modifications.
